\documentclass[a4paper, 12pt]{article}

\title{Report 1}
\author{Ali Abolhassanzadeh Mahani}

\begin{document}
	\section{Progress}
	\begin{itemize}
		\item We found a way to implement the whole process without the use of 
		the \textit{event-based} method in \texttt{Python}.
		
		\item The python version is written by dividing the time step into a homogeneous 
		and an in-homogeneous part. the homogeneous is obvious integration and 
		the in-homogeneous section is almost like event-based. 
		
		\item I started implementing the system in \texttt{C++}. In this language I can
		make the implementation \textit{event-based}. 
		I created a class \texttt{Neuron} as a new level of abstraction for the system.
		The system will then contain Neurons and using the functions that will be written
		for \texttt{Neuron} and \texttt{Nervous System}, I will implement the system.
		
		\item Completely implemented the dynamics of the neural network in C++.
		The dynamics are event-based as they are a result of the interactions between the
		network and the neurons.
		
		\item Added file stream and output of data to \texttt{.csv} files in C++.\\
		Also added the \texttt{cleandat} .PHONY to the \texttt{Makefile} to clean all the data if used.
		
		\item Added the calculation and report of mean area intersection to \texttt{.csv} files.
		Now I'm running the code for $10^5$ seconds. \\
		Ok. The simulation seems to be working well but the duration was apparently a bit short and 
		the plots showed that the system didn't reach stability.
		
		\item I optimized the \texttt{calc\_mutual\_area()} method and will now run the program for 
		a duration of $5 \times 10^5 s$ and wait for the results.
	\end{itemize}

	\section{Problems}
	\begin{itemize}
		\item The \texttt{python} version doesn't work. I assume there is something
		wrong with the constants defined in the system; but still, anything is possible.
		
		\item The plots for $g\tau A_{i}$ don't come out as what we expect and for 
		the first run that took about $160000$ seconds, the values flew into a small 
		value of order $\mathcal{O}(10^{-2})$ and oscillated about those values for
		the rest of the time.

		\item By test run 4 which had varied the parameters quite a bit to exaggerate the logical bugs,
		I found out that in the \texttt{C++} version, the neurons \textbf{Never} fire, not even once! Which 
		suggests that there is something wrong with the random generation process for firing neurons.
	\end{itemize}

	\section{Ideas}
	
\end{document}